---
title: "Business Intelligence Project"
author: "Challengers"
date: "6th November 2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---
# Students Details

|                                              |     |
|----------------------------------------------|-----|
|                                              |     |
| **Student ID Number**                        | 124255,120415,124562,118211,124422 |
| **Student Name**                             | Natasha Gichira, Emmanuel Agre, Ryan Gitonga,Fredrick Koech, Dennis Muriuki |
| **BBIT 4.2 Group**                           | C |
| **BI Project Group Name/ID (if applicable)** | Challengers |

# Setup Chunk


**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```
# STEP 1. Install and Load the Required Packages ----
#Load the language server first
```{r}

if (require("languageserver")) {
  require("languageserver")
} else {
  install.packages("languageserver", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## kernlab ----
if (require("kernlab")) {
  require("kernlab")
} else {
  install.packages("kernlab", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## randomForest ----
if (require("randomForest")) {
  require("randomForest")
} else {
  install.packages("randomForest", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```
# STEP 2. Load the Dataset ----
#This dataset is already included in R
```{r}
data("iris")
```
#Check for any missing values in the dataset
```{r}
anyNA(iris)
```

# STEP 3. The Resamples Function ----
```{r}
## 3.a. Train the Models ----
# We train the following models, all of which are using 10-fold repeated cross
# validation with 3 repeats:
#   LDA
#   CART
#   KNN
#   SVM
#   Random Forest

train_control <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

### LDA ----
set.seed(7)
iris_model_lda <- train(Species ~ ., data = iris,
                            method = "lda", trControl = train_control)

### CART ----
set.seed(7)
iris_model_cart <- train(Species ~ ., data = iris,
                             method = "rpart", trControl = train_control)

### KNN ----
set.seed(7)
iris_model_knn <- train(Species ~ ., data = iris,
                            method = "knn", trControl = train_control)

### SVM ----
set.seed(7)
iris_model_svm <- train(Species ~ ., data = iris,
                            method = "svmRadial", trControl = train_control)

### Random Forest ----
set.seed(7)
iris_model_rf <- train(Species ~ ., data = iris,
                           method = "rf", trControl = train_control)
## 3.b. Call the `resamples` Function ----
# We then create a list of the model results and pass the list as an argument
# to the `resamples` function.

results <- resamples(list(LDA = iris_model_lda, CART = iris_model_cart,
                          KNN = iris_model_knn, SVM = iris_model_svm,
                          RF = iris_model_rf))
```

# STEP 4. Display the Results ----
```{r}
## 1. Table Summary ----
# This is the simplest comparison. It creates a table with one model per row
# and its corresponding evaluation metrics displayed per column.
summary(results)

## 2. Box and Whisker Plot ----
# This is useful for visually observing the spread of the estimated accuracies
# for different algorithms and how they relate.
scales <- list(x = list(relation = "free"), y = list(relation = "free"))
bwplot(results, scales = scales)

## 3. Dot Plots ----
# They show both the mean estimated accuracy as well as the 95% confidence
# interval (e.g. the range in which 95% of observed scores fell).
scales <- list(x = list(relation = "free"), y = list(relation = "free"))
dotplot(results, scales = scales)

## 4. Scatter Plot Matrix ----
# This is useful when considering whether the predictions from two
# different algorithms are correlated. If weakly correlated, then they are good
# candidates for being combined in an ensemble prediction.
splom(results)

## 5. Pairwise xyPlots ----
# You can zoom in on one pairwise comparison of the accuracy of trial-folds for
# two models using an xyplot.
xyplot(results, models = c("LDA", "SVM"))

# or
xyplot(results, models = c("SVM", "CART"))

## 6. Statistical Significance Tests ----
# This is used to calculate the significance of the differences between the
# metric distributions of the various models.

### Upper Diagonal ----
# The upper diagonal of the table shows the estimated difference between the
# distributions. If we think that LDA is the most accurate model from looking
# at the previous graphs, we can get an estimate of how much better it is than
# specific other models in terms of absolute accuracy.

### Lower Diagonal ----
# The lower diagonal contains p-values of the null hypothesis.
# The null hypothesis is a claim that "the models are the same".
# A lower p-value is better (more significant).

diffs <- diff(results)

summary(diffs)
```